### 2014-03-28 tex/main-body-text.tex
expand introduction and start putting in basic structure

>>>>

Methods for the unsupervised clustering of genotypes has received 
considerable attention in the molecular ecology literature.  
The best known example of this class of methods is {\sc structure} 
\citep{Pritchardetal2000}.  {\sc structure} itself can be interpreted 
as an elaboration of earlier models used to identify the spawning 
stock of salmon \citep{Smouseetal1990}, and a variety of other 
clustering methods have been developed that are all closely related to 
{\sc structure}, for example {\sc NewHybrids} \citep{And&Tho2002}, {\sc 
BayesAss+} \citep{Wil&Ran2003}, and {\sc baps} 
\citep{Coranderetal2004}. (An overview of these similarities can be 
found in \citealt{Anderson2009PGAC})

\section*{Comparison of methods}

\subsection*{{\sc flock}}
One issue I have with it is that it is described as a ``procedure'' or 
an ``algorithm,'' without an attempt to see it as a special case of 
well known inference frameworks.

Some quotations to ponder.
\begin{itemize}
\item ``FLOCK is a non- Bayesian method and therefore differs 
substantially from previous clustering algorithms''(p.~1333)

\item ``However, its working principle does not involve a probabilistic 
walk through the space of all possible k-partitions of sample S as is 
the case with clustering algorithms such as Structure (Pritchard et al. 
2000), BAPS (Corander et al. 2003) and NewHybrids (Anderson \& Thompson 
2002).''(p.~1334).

\item ``Partition (Dawson \& Belkhir 2001) is another clustering 
program. However, since it is assuming Hardy–Weinberg and linkage 
equilibrium, it is not suitable for the analysis of samples originating 
from genetic groups in the process of becoming admixed.''(p.~1334).

\item In \citet{Duc&Tur2012}: ``Note that FLOCK is very different from 
other clustering 
programs. It does not sample the space of partitions through small 
random step walks as in MCMC, and it does not try to optimize some 
target function, such as HWLE. Briefly stated, it is not based on a 
probabilistic search algorithm. On the contrary, FLOCK is 
entirely deterministic.''(p.~736).

\end{itemize}

\subsection*{{\sc structure}}

\subsection*{{\sc flock} as a special case of {\sc structure}}

\section*{Conclusions}
